\cvsection{Professional Experience}

\begin{cventries}
  \cventry
    {Software Engineer II} % Job title
    {The Home Depot} % Organization
    {Atlanta, GA} % Location
    {September 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develop new Java/Spring-based features for cloud-based customer data privacy micro-services supporting back-end APIs.}
        \item {Develop automated reporting tools using Google Cloud Platform services for use by internal operations teams.}
        \item {Develop custom user interface components/web pages displayed on \href{https://www.homedepot.com/privacy/mypreferencecenter}{homedepot.com.}}
        \item {Support production applications, troubleshooting issues as necessary.}
        \item {Develop new unit and integration test suites for microservice applications.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer} % Job title
    {Capital One} % Organization
    {Washington, DC} % Location
    {February 2020 - August 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built and managed cloud-based ETL pipelines performing feature extraction/model
        scoring used to measure credit risk for a \$4 billion portfolio.}
        \item {Redesigned and refactored feature extraction modules to a class-based design, reducing
        per-repository LOC by 50\% and consolidating configuration items into one repository to reduce
        maintenance overhead.}
        \item {Implemented re-optimizations to Spark dataframe manipulations/Spark job configurations, reducing
        processing time for model scoring by 50\%.}
        \item {Designed and built new features for cloud-based session management microservices.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer Intern} % Job title
    {Capital One} % Organization
    {Washington, DC} % Location
    {June 2019 - August 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and built a Scala API facilitating access to the enterprise-wide Kafka platform by
        consumer applications.}
        \item {Using Spring Boot, designed and built a RESTful Kafka producer program for data obtained from
        one of Capital One’s identity and access management applications, enabling real-time access
        to customer site-navigation behavior.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer Intern} % Job title
    {Nuesoft Technologies} % Organization
    {Atlanta, GA} % Location
    {March 2018 - August 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and built a Python ETL application facilitating the
        transfer of patient medical chart data from new client legacy platforms to Nuesoft servers, replacing a manual process and reducing chart data transfer time from 2 weeks to 1 day.}
      \end{cvitems}
    }

\end{cventries}
